Nabi - A Preventative Solution Against JavaScript and Scriptless Tabnabbing Attacks

### 2015-05-05 paper/paper.tex
I spell bad

We have devleoped a system to block tabnabbing attacks that still allows the user to retain most of the javascript functionality they need to securly browse the internet while without just only detecting and alerting the user.

>>>>

We have devloped a system to block tabnabbing attacks that still allows the user to retain most of the JavaScript functionality they need to securely browse the Internet while without just only detecting and alerting the user.
